\section{Summary} \label{cap:summary}
"Sanji's Baratie" is a fictional restaurant database inspired by the culinary world of Sanji based on the “One Piece" series. It envisions a meticulously crafted database that captures the essence of Sanji’s restaurant on an enchanting island. The primary objective of this database is to facilitate data retrieval, ensure data integrity and security, data analysis, maintenance, and application integration. Users of the database include Sanji, restaurant staff, customers, managers, and potential investors/partners. The database stores information related to employees, customers, vendors, orders, dishes, ingredients, inventory, bills, tables, restock orders, feedback, and reservations. It maintains strong entity types, such as employees, customers, vendors, orders, dishes, inventory, bills, tables, restock orders, and feedback. Additionally, it defines various binary and degree > 2 relationship types to link these entities.
Functional requirements encompass data modification and retrieval tasks. Users can insert new customer and order details, add dishes to the menu, include new vendors, and recruit employees. Deletion involves removing dishes from the menu, and updates allow for changes in dish/ingredient prices, vendor payment statuses, and employee salaries. Retrievals include data selection, analysis, and aggregation to generate insights, such as calculating average salaries and tracking financial performance. \\
Thus, "Sanji's Baratie" database aims to provide a comprehensive and efficient platform for managing a restaurant's operations, from customer interactions to menu items, inventory, and financial transactions, while embracing the spirit of the "One Piece" universe.