\section{Users} \label{cap:model}


The users of the "Sanji's Baratie" database are:
\begin{enumerate}
    \item \underline{\textbf{Sanji (Restaurant Owner and Chef):}} Sanji himself would use the database to manage the restaurant's menu, track customer preferences, monitor orders, and oversee the performance of his staff. He could use it to refine his culinary offerings and enhance the restaurant's overall experience.
    \item \underline{\textbf{Restaurant Staff:}} The waitstaff and kitchen staff would use the database to fulfill customer orders, update the menu as needed, and coordinate their roles within the restaurant.
    \item \underline{\textbf{Customers:}} Frequent patrons or visitors to Sanji's restaurant could use the database to view the menu, place orders, and provide feedback or reviews on their dining experiences.
    \item \underline{\textbf{Restaurant Managers:}} If there are managers or supervisors overseeing the restaurant's operations, they could use the database to monitor staff performance, track sales, and make managerial decisions. They can also use this data to check what all raw materials vegetables and spices would be required and place order accordingly. They can also keep track of staff's rating and based on the rating can increment or decrement some staff persons salary or recruit/fire staff.
    \item \underline{\textbf{Potential Investors or Partners:}} If Sanji's restaurant were seeking investments or partnerships, potential stakeholders might use the database to assess the restaurant's performance and prospects.
\end{enumerate}